
% ==============================================================================
% PhD Curriculum Vitae — High-Density Template
% ==============================================================================
\documentclass[10pt, letterpaper]{article}

%------------------------------------------------------------------------------
% Packages
%------------------------------------------------------------------------------
\usepackage[margin=0.75in, top=0.65in, bottom=0.65in]{geometry}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{array}
\usepackage{xcolor}
\usepackage{microtype}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{ifthen}
\usepackage{amssymb}

%------------------------------------------------------------------------------
% Colors
%------------------------------------------------------------------------------
\definecolor{accentblue}{RGB}{20, 75, 140}
\definecolor{darkgray}{RGB}{40, 40, 40}
\definecolor{lightgray}{RGB}{120, 120, 120}
\definecolor{rulecolor}{RGB}{180, 200, 225}
\definecolor{RULECOLOR}{RGB}{180, 200, 225}

%------------------------------------------------------------------------------
% Hyperref
%------------------------------------------------------------------------------
\hypersetup{colorlinks=true, urlcolor=accentblue, linkcolor=accentblue, pdfborder={0 0 0}}

%------------------------------------------------------------------------------
% Spacing — tighter everywhere
%------------------------------------------------------------------------------
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}

%------------------------------------------------------------------------------
% Section formatting
%------------------------------------------------------------------------------
\titleformat{\section}
  {\normalsize\bfseries\color{accentblue}\uppercase}
  {}{0em}{}
  [\vspace{-5pt}\textcolor{rulecolor}{\rule{\linewidth}{0.5pt}}\vspace{1pt}]
\titlespacing{\section}{0pt}{8pt}{3pt}

\titleformat{\subsection}
  {\small\bfseries\color{darkgray}}
  {}{0em}{}[]
\titlespacing{\subsection}{0pt}{4pt}{1pt}

%------------------------------------------------------------------------------
% List settings — compact
%------------------------------------------------------------------------------
\setlist{noitemsep, topsep=1pt, parsep=0pt, partopsep=0pt}
\setlist[itemize]{leftmargin=1.2em, label=\textcolor{accentblue}{\textbullet}}
\setlist[enumerate]{leftmargin=1.6em}

%------------------------------------------------------------------------------
% Custom commands
%------------------------------------------------------------------------------
\newcommand{\entry}[3]{%
  \begin{tabularx}{\linewidth}{@{}X r@{}}
    \textbf{#1} \textcolor{lightgray}{$\cdot$} \textit{#2} &
    {\small\textcolor{lightgray}{#3}}
  \end{tabularx}\vspace{1pt}%
}

\newcommand{\entrysub}[4]{%
  \begin{tabularx}{\linewidth}{@{}X r@{}}
    \textbf{#1} \textcolor{lightgray}{$\cdot$} \textit{#2} &
    {\small\textcolor{lightgray}{#3}}
  \end{tabularx}%
  \ifthenelse{\equal{#4}{}}{}{\\\hspace{1.2em}{\small\textcolor{darkgray}{#4}}}%
  \vspace{1pt}%
}

\newcommand{\honorrow}[3]{%
  \begin{tabularx}{\linewidth}{@{}X r@{}}
    #1 \textcolor{lightgray}{$\cdot$} \textit{\small #2} & {\small\textcolor{lightgray}{#3}}
  \end{tabularx}\vspace{1pt}%
}

%==============================================================================
\begin{document}
\pagestyle{empty}

%==============================================================================
% HEADER
%==============================================================================
\begin{center}
  {\Large\bfseries\color{darkgray} Your Full Name}\\[3pt]
  {\small\color{lightgray}
    Ph.D. Candidate $\cdot$ Department of Computer Science $\cdot$ University of Somewhere\\[2pt]
    \faEnvelope[regular]\;\href{mailto:you@university.edu}{you@university.edu}\quad
    \faGlobe\;\href{https://yoursite.com}{yoursite.com}\quad
    \faGithub\;\href{https://github.com/you}{github.com/you}\quad
    \faLinkedin\;\href{https://linkedin.com/in/you}{linkedin.com/in/you}\quad
    \faMapMarker*\;City, Country
  }
\end{center}
\vspace{2pt}

%==============================================================================
% RESEARCH INTERESTS
%==============================================================================
\section{Research Interests}

\textbf{Machine learning} and \textbf{natural language processing}, with emphasis on
\textbf{efficient fine-tuning} of large language models, \textbf{model interpretability},
\textbf{low-resource and cross-lingual transfer}, and applications of LLMs to
\textbf{biomedical and scientific text mining}.
Broadly interested in scaling laws, alignment, and evaluation methodology.

%==============================================================================
% EDUCATION
%==============================================================================
\section{Education}

\entrysub{Ph.D., Computer Science}{University of Somewhere}{Sep 2020 -- Present (expected May 2025)}%
  {Advisor: Prof.\ Jane Doe \quad Dissertation: \textit{Efficient and Interpretable LLMs for Scientific Text} \quad GPA: 4.0/4.0}

\entrysub{M.S., Computer Science}{University of Somewhere}{Sep 2018 -- May 2020}%
  {Thesis: \textit{Graph Neural Networks for Knowledge Base Completion} \quad GPA: 3.95/4.0}

\entrysub{B.Eng., Software Engineering (Hons.)}{Tsinghua University, Beijing}{Sep 2014 -- Jun 2018}%
  {Graduated with Distinction, ranked 3rd/120 \quad Dean's List all semesters \quad National Scholarship 2016, 2017}

%==============================================================================
% SELECTED PUBLICATIONS
%==============================================================================
\section{Selected Publications}
{\small\textcolor{lightgray}{$^\dagger$equal contribution.\quad
\faExternalLink*\;\href{https://scholar.google.com/}{Full list on Google Scholar.}}}
\vspace{2pt}

\begin{enumerate}[label={\small[\arabic*]}, itemsep=3pt, topsep=0pt]

  \item \textbf{Your Name}, Author B, Author C, Jane Doe.
    ``Efficient Fine-Tuning of Large Language Models via Sparse Adapters.''
    \textit{Proc.\ ACL} \textbf{2024} (long paper, oral presentation), Bangkok.
    [\href{https://arxiv.org/}{arXiv}][\href{https://github.com/}{Code}][\href{https://}{Slides}]

  \item Author A$^\dagger$, \textbf{Your Name}$^\dagger$, Jane Doe.
    ``Low-Resource NER with Contrastive Curriculum Learning.''
    \textit{Proc.\ EMNLP} \textbf{2023} (long), Singapore.
    [\href{https://arxiv.org/}{arXiv}][\href{https://github.com/}{Code}]

  \item \textbf{Your Name}, Jane Doe.
    ``Interpretable Sparse Attention for Scientific Document Understanding.''
    \textit{Transactions of ACL} (\textbf{TACL}), vol.\ 11, pp.\ 345--360, \textbf{2023}.
    [\href{https://arxiv.org/}{arXiv}][\href{https://github.com/}{Demo}]

  \item \textbf{Your Name}, Author B, Jane Doe.
    ``Knowledge-Augmented LLMs for Biomedical QA.''
    \textit{BioNLP Workshop @ NAACL} \textbf{2022}.\;
    \textcolor{accentblue}{\textbf{Best Paper Award.}}
    [\href{https://arxiv.org/}{arXiv}]

  \item Author C, \textbf{Your Name}, Author D.
    ``Retrieval-Augmented Scientific Claim Verification.''
    \textit{Findings of EMNLP} \textbf{2022}.
    [\href{https://arxiv.org/}{arXiv}][\href{https://github.com/}{Code}]

\end{enumerate}

\noindent{\small\textit{\textcolor{lightgray}{Under Review / Preprints:}}}
\begin{enumerate}[label={\small[\arabic*]}, itemsep=2pt, topsep=1pt, start=6]
  \item \textbf{Your Name}, Author E, Jane Doe.
    ``Scaling Laws for Domain-Adaptive Pre-Training.''
    Submitted to \textit{NeurIPS 2024}.
    [\href{https://arxiv.org/}{arXiv}]

  \item Author F, \textbf{Your Name}.
    ``Benchmark Contamination Detection via Membership Inference.''
    Preprint, \textbf{2024}. [\href{https://arxiv.org/}{arXiv}]
\end{enumerate}

%==============================================================================
% RESEARCH EXPERIENCE
%==============================================================================
\section{Research Experience}

\entry{Graduate Research Assistant}{NLP Lab, University of Somewhere}{Aug 2020 -- Present}
\begin{itemize}
  \item Developed sparse-adapter fine-tuning framework; reduced training FLOPs by 60\% with $<$0.3\% accuracy drop across 8 GLUE tasks; open-sourced with \textbf{5.2k GitHub stars}, adopted by 25+ research labs worldwide.
  \item Designed contrastive curriculum learning strategy for low-resource NER; achieved new SOTA on 6 of 7 benchmarks (CoNLL-2003, WNUT-17, etc.) under 100-example setting.
  \item Mentored 4 undergraduates and 2 M.S.\ students; 2 became co-authors on published conference papers.
  \item Authored successful \$45k NSF ACCESS compute proposal; managed cluster allocations for lab-wide experiments.
\end{itemize}
\vspace{3pt}

\entry{Visiting Researcher (host: Prof.\ C.\ Manning)}{Stanford NLP Group}{Jun -- Aug 2023}
\begin{itemize}
  \item Investigated zero-shot cross-lingual transfer across 30+ languages via language-neutral representation learning.
  \item Results integrated into ACL 2024 submission; contributed 3k-line patch to Stanford CoreNLP.
\end{itemize}
\vspace{3pt}

\entry{Research Intern (host: Dr.\ X)}{Allen Institute for AI (AI2), Seattle}{May -- Aug 2022}
\begin{itemize}
  \item Built scientific claim verification pipeline on S2ORC (136M papers); F1 +4.2 pts over prior SOTA (Wadden et al.).
  \item Deployed as live demo serving 500+ daily active users; published in Findings of EMNLP 2022.
\end{itemize}

%==============================================================================
% INDUSTRIAL EXPERIENCE
%==============================================================================
\section{Industrial Experience}

\entry{Research Intern --- Gemini Pre-training Team}{Google DeepMind, London, UK}{Jun -- Sep 2022}
\begin{itemize}
  \item Contributed to Gemini pre-training data pipeline running on TPU v4 pods (10k+ chips, multi-datacenter).
  \item Designed domain-weighted data-mixing curriculum: +2.3\% MMLU, +1.8\% BIG-Bench Hard vs.\ flat-mixing baseline.
  \item Co-authored internal technical report; methodology adopted in subsequent production training runs.
\end{itemize}
\vspace{3pt}

\entry{Machine Learning Intern --- FAIR}{Meta AI Research, Menlo Park, CA}{Jun -- Aug 2021}
\begin{itemize}
  \item Prototyped RAG system for internal enterprise knowledge search (200k+ docs, 10k+ daily queries).
  \item Reduced P95 retrieval latency by 35\% via HNSW indexing + query-side embedding cache; shipped to 1k users.
  \item Filed U.S.\ patent application on learned sparse retrieval (pending, App.\ \#18/123,456).
\end{itemize}
\vspace{3pt}

\entry{Software Engineering Intern --- Search Infrastructure}{Baidu, Beijing}{Jun -- Aug 2017}
\begin{itemize}
  \item Optimized inverted index compression scheme; 12\% index size reduction on a 20B-document production corpus.
\end{itemize}

%==============================================================================
% TEACHING & SERVICE
%==============================================================================
\section{Teaching \& Service}

\subsection*{Teaching}
\begin{itemize}
  \item \textbf{Head TA}, CS 6741 Natural Language Processing (Grad, $\sim$120 students), Univ.\ of Somewhere\hfill\textcolor{lightgray}{\small Fall 2022, 2023}
  \item \textbf{Teaching Assistant}, CS 4120 Introduction to Machine Learning\hfill\textcolor{lightgray}{\small Spring 2021}
  \item \textbf{Guest Lecturer}: ``Transformers \& Self-Attention'' (CS 4120, Mar 2023); ``Parameter-Efficient Fine-Tuning'' (CS 6741, Oct 2023)
  \item \textbf{Lecturer}, 3-day bootcamp ``Practical LLMs for Scientists'', AI for Science Summer School, Jul 2023 (60 attendees)
\end{itemize}

\subsection*{Academic Service}
\begin{itemize}
  \item \textbf{Reviewer}: ACL (2022--2024), EMNLP (2021--2023), NeurIPS (2022--2024), ICLR (2023--2024), NAACL 2024, TACL, JMLR; ACL ARR rolling (2022--present) \quad \textcolor{accentblue}{\textbf{Outstanding Reviewer, ACL 2023}}
  \item \textbf{Area Chair / Meta-Reviewer}: ACL Rolling Review, Jan--Mar 2024
  \item \textbf{Session Chair}: NLP Applications Track, ACL 2023; Efficient NLP Track, EMNLP 2023
  \item \textbf{Organizer}: NLP Reading Group, Univ.\ of Somewhere (weekly, 30+ participants), 2021--present
  \item \textbf{PhD Admissions Committee}, Dept.\ of CS, Univ.\ of Somewhere, 2022--2023
  \item \textbf{Student Volunteer}: ACL 2021, NeurIPS 2020
\end{itemize}

%==============================================================================
% HONORS & AWARDS
%==============================================================================
\section{Honors \& Awards}

\honorrow{Outstanding Paper Award}{ACL 2024}{2024}
\honorrow{Outstanding Reviewer Award}{ACL 2023}{2023}
\honorrow{NSF Graduate Research Fellowship (GRFP), 3-year full support}{National Science Foundation}{2020--2023}
\honorrow{University Graduate Fellowship (full tuition + stipend)}{University of Somewhere}{2020}
\honorrow{Google PhD Fellowship --- Finalist, NLP track}{Google}{2021}
\honorrow{Best Paper Award}{Workshop on Biomedical NLP @ NAACL 2022}{2022}
\honorrow{NSF ACCESS Compute Allocation Grant (\$45k GPU hours)}{National Science Foundation}{2022}
\honorrow{Undergraduate Excellence Award --- Dept.\ Gold Medal, Top 3\%}{Tsinghua University}{2018}
\honorrow{National Scholarship (top 1\% nationwide, awarded twice)}{Ministry of Education, China}{2016, 2017}

%==============================================================================
% MISCELLANEOUS
%==============================================================================
\section{Miscellaneous}

\begin{tabularx}{\linewidth}{@{}>{\bfseries\small}p{2.5cm}X@{}}
  Programming   & Python, C++, CUDA, Bash, SQL, Julia \\[1.5pt]
  ML Frameworks & PyTorch, JAX/Flax, Hugging Face (Transformers, PEFT, Datasets, Accelerate), DeepSpeed, vLLM, TRL \\[1.5pt]
  Infrastructure & Git, Docker/Singularity, Slurm, AWS (EC2/S3), GCP, Weights \& Biases, Ray, Kubernetes \\[1.5pt]
  Languages     & English (fluent), Mandarin Chinese (native), French (intermediate, DELF B2) \\[1.5pt]
  Open Source   & Maintainer: \href{https://github.com/}{SparseAdapt} (5.2k $\bigstar$, 300+ forks); contributor: HF Transformers, AllenNLP \\[1.5pt]
  Interests     & Marathon running (PB 3:12:04), landscape photography, science communication (blog: 2k subscribers) \\[1.5pt]
  References    & Prof.\ Jane Doe (advisor, advisor@univ.edu) $\cdot$ Prof.\ C.\ Manning (Stanford) $\cdot$ Dr.\ X (Google DeepMind) \\
\end{tabularx}

\vspace{8pt}
\noindent\textcolor{lightgray}{\footnotesize\textit{Last updated: \today}}

\end{document}

